Learning Discrete-valued Bayesian Networks from Mixed Data

### 2015-11-17 BN_discretizer_paper.tex
change caption

Figure \ref{fig:wine_graph_2} is the learned discrete-valued Bayesian network from the Wine dataset, and it is obtained by running Algorithm \ref{alg:structure_learn} 50 times. The integer numbers next to variables are cardinality numbers of variables. By comparing Figure \ref{fig:wine_graph_2} with \ref{fig:wine_graph_1}, it shows that the the Bayesian network obtained by \ref{alg:structure_learn} has more edges than the network obtained by prediscretization and the K2 algorithm. Furthermore, the cardinalitis of discretized variables in Figure \ref{fig:wine_graph_2} are smaller than the result in \ref{fig:wine_disc_table_1}.

@@

\begin{figure}[ht]
    \begin{tabular}{cc}
      \input{graph_wine_exp2_distr_5_11}
    \end{tabular}
  \caption{Comparison of the raw data and discretization result on variable $E$ and $K$ according to Figure \ref{Auto_graph_2}}
  \label{fig:wine_exp2_distr}
\end{figure}

>>>>

Figure \ref{fig:wine_graph_2} is the learned discrete-valued Bayesian network from the Wine dataset, and it is obtained by running Algorithm \ref{alg:structure_learn} 50 times. The integer numbers next to variables are cardinality numbers of variables. By comparing Figure \ref{fig:wine_graph_2} with \ref{fig:wine_graph_1}, it shows that the the Bayesian network obtained by \ref{alg:structure_learn} has more edges than the network obtained by prediscretization and the K2 algorithm. Furthermore, the cardinalitis of discretized variables in Figure \ref{fig:wine_graph_2} are smaller than the result in \ref{table:wine_disc_table_1}.

@@

\begin{figure}[ht]
    \begin{tabular}{cc}
      \input{graph_wine_exp2_distr_5_11}
    \end{tabular}
  \caption{The discretization result on variable $E$ and $K$ of the learned network in Figure \ref{fig:wine_graph_2}}
  \label{fig:wine_exp2_distr}
\end{figure}
